R Markdown for Reproducible Research

### 2019-01-07 paper.Rmd
add parameterized r markdown section

A little known feature of R Markdown is the ability to add _parameters_.
Parameterized R Markdown is defined by adding parameters to the YAML header,
which will then be utilized within the rendering of the document.

>>>>

A little known feature of R Markdown is the ability to add _parameters_.
Parameterized R Markdown is defined by the addition of parameters to the YAML
header, which will then be utilized within the rendering of the document.

For instance, a YAML header like the following might be used to define the
report dates:

```yaml
---
title: "R Markdown - Parameterized"
output: html_document
params:
  start_date: !r Sys.Date() - 10
  end_date: !r Sys.Date()
---
```

This allows these values to be accessible in code using `params$start_date` and
`params$end_date`. It essentially makes the R Markdown document a _parameterized
executable_ or function, which can then be called using `rmarkdown::render()`.
For example, the following executes this R Markdown report with non-default
parameter selections:

```r
rmarkdown::render(
  "./ex/ex-parameterized.Rmd", 
  params = list(
    start_date = Sys.Date()-5, 
    end_date = Sys.Date()
  )
)
```

There is [much more](todo) available to explore in Parameterized R Markdown,
like an easy-to-use [user interface](todo) for selecting values. You can also
host Parameterized R Markdown in a publishing platform like RStudio Connect that
exposes a user interface to end users of a report.
